HFI in RISC-V

### 2025-03-26 paper.tex

\section{Related Work}
Several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata such as Donky \cite{Donky}, whi

>>>>

\section{Related Work}
Several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata such as Donky \cite{Donky}, whi
Our work on HFI for RSIC-V builds on prior work that established HFI for x86-64 architectures \cite{HFI}. 
There are also several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata to store a per-sandbox ID checked by hardware, such as Donky \cite{Donky} or IMIX \cite{IMIX}. Donky has been implemented for both x86 and RISC-V architectures, while IMIX has only been implemented on x86. In addition to this, there are also methods that make use of capability-based addressing, a m, which is seen most prominently in Cheri \cite{CHERI}, which has been implemented for RISC-V. While Cheri is a strong security model, it requires extensive modification of the software, and hardware including the OS, ABI, and compiler.
